A Process for Emulating Comparative Oncology Trials with Real-world Evidence Studies (ENCORE): Process Development and Methodological Considerations for Oncology Real-World Data

### 2025-03-30 manuscript/manuscript.qmd
typo

[**Manuscript word count:**]{.underline} 4,131 words / 8,000 words

[**Abstract word count:**]{.underline} 248 words / 250 words

@@

-   Primary purpose was study treatment efficacy

>>>>

[**Manuscript word count:**]{.underline} 4,200 words / 8,000 words

[**Abstract word count:**]{.underline} 224 words / 250 words

@@

-   Primary purpose was to study treatment efficacy
